Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2022-12-19 src/tex/ms.tex
Unlock figures and fix simon stevenson's citation

% \begin{figure*}[h]
%     \includegraphics[width=\textwidth]{figures/GW150914_corner_zoomed_lowres.png}
%     \caption{The posterior for GW150914 in both the progenitor parameter space
%     and hyperparameter space. $M_1$ and $M_2$ are the progenitors' masses.
%     $\log{Z}$ is log metallicity at ZAMS. $z$ is the redshift at ZAMS. $\alpha$
%     is the common envelope efficiency. $f_{\rm acc}$ is the fraction of mass
%     accreted during stable mass transfer. $q_{\rm crit, 3}$ is the critical mass
%     ratio on the Hertzsprung Gap. The contours correspond to the $68\%$ and
%     $95\%$ confidence intervals. Note that the redshift is not fitted during the
%     root finding process or the MCMC process. Once we find the evolutionary
%     parameters, we add the delay time to the lookback time of the observed
%     posterior sample, then from the total lookback time we can compute the
%     redshift at ZAMS. We highlight three panels in the corner plots to show the
%     fine structure of the set of posterior samples in the evolutionary parameter
%     space. We also color the posterior in a particular panel according to the
%     type of parameters involved in the corner plot. Blue denotes panels that
%     include only progenitor parameters, green denotes panels that include a mix
%     of progenitor parameters and hyperparameters, and orange denotes panels that
%     include only hyperparameters. }
%     \label{fig:GW150914_posterior}
%     \script{figure1_cornerPlot.py}
% \end{figure*}

@@

% \begin{figure*}
%     \includegraphics[width=0.98\textwidth]{figures/compare_fixed_variable.png}
%     \caption{Comparison of ZAMS masses for binaries which produce GW150914-like
%      mergers for three variations of $\alpha$ with a fixed set of parameter
%      assumptions matching those of A21 (first three columns) and for binaries
%      which produce GW150914-like mergers when $\alpha$, $f_{\mathrm{acc}}$, and
%      $q_{crit,3}$ are allowed to vary, (fourth column).}
%     \label{fig:compare_fixed_variable}
%     \script{figure2_varyAlphaFacc.py}
% \end{figure*}

@@

% \begin{figure}
% \includegraphics[width=0.49\textwidth]{figures/GW150914_reprojection.pdf}
% \caption{Reprojecting the posterior in evolutionary parameter space of GW150914
% to observable space. The contours correspond to the $68\%$ and $95\%$ confidence
% intervals. The blue contour is the reprojected posterior after the root-finding
% procedure. The orange contour is the reprojected posterior after the MCMC
% procedure. The green contour is the posterior plotted using the original LVK
% posterior samples. }
% \label{fig:GW150914_reprojection}
% \script{figure3_sanityCheck.py}
% \end{figure}

@@

% \begin{figure}
% \includegraphics[width=0.49\textwidth]{figures/GWTC3_f_acc_mass.pdf}
% \caption{ The posterior density in the $m_{1,{\rm GW}}-f_{\rm acc}$ space for
%     most of the events in GWTC-3. Note that $m_{1,{\rm GW}}$ here refers to the
%     reprojected posterior instead of the posterior released by LIGO. Each
%     contour is the $68\%$ credible interval of the posterior density for a
%     particular event. At $m_{1,{\rm GW}} \sim 45 M_{\odot}$, the pair
%     instability supernova mechanism prevents \texttt{COSMIC} from producing
%     events that are more massive than this cutoff. Therefore, events with the
%     majority of posterior support above this cutoff are not compatible with
%     \texttt{COSMIC}, hence have a large KL divergence and are excluded from this
%     figure. On the low mass end, neutron star binaries or neutron star-black
%     hole binaries are subjected to randomness induced by the natal kick, also
%     resulting in a larger and fluctuating KL divergences, and therefore are also
%     excluded from the analysis. }
% \label{fig:GWTC-3_f_acc_mass}
% \script{figure4_population.py}
% \end{figure}

>>>>

\begin{figure*}[h]
    \includegraphics[width=\textwidth]{figures/GW150914_corner_zoomed_lowres.png}
    \caption{The posterior for GW150914 in both the progenitor parameter space
    and hyperparameter space. $M_1$ and $M_2$ are the progenitors' masses.
    $\log{Z}$ is log metallicity at ZAMS. $z$ is the redshift at ZAMS. $\alpha$
    is the common envelope efficiency. $f_{\rm acc}$ is the fraction of mass
    accreted during stable mass transfer. $q_{\rm crit, 3}$ is the critical mass
    ratio on the Hertzsprung Gap. The contours correspond to the $68\%$ and
    $95\%$ confidence intervals. Note that the redshift is not fitted during the
    root finding process or the MCMC process. Once we find the evolutionary
    parameters, we add the delay time to the lookback time of the observed
    posterior sample, then from the total lookback time we can compute the
    redshift at ZAMS. We highlight three panels in the corner plots to show the
    fine structure of the set of posterior samples in the evolutionary parameter
    space. We also color the posterior in a particular panel according to the
    type of parameters involved in the corner plot. Blue denotes panels that
    include only progenitor parameters, green denotes panels that include a mix
    of progenitor parameters and hyperparameters, and orange denotes panels that
    include only hyperparameters. }
    \label{fig:GW150914_posterior}
    \script{figure1_cornerPlot.py}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=0.98\textwidth]{figures/compare_fixed_variable.png}
    \caption{Comparison of ZAMS masses for binaries which produce GW150914-like
     mergers for three variations of $\alpha$ with a fixed set of parameter
     assumptions matching those of A21 (first three columns) and for binaries
     which produce GW150914-like mergers when $\alpha$, $f_{\mathrm{acc}}$, and
     $q_{crit,3}$ are allowed to vary, (fourth column).}
    \label{fig:compare_fixed_variable}
    \script{figure2_varyAlphaFacc.py}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.49\textwidth]{figures/GW150914_reprojection.pdf}
\caption{Reprojecting the posterior in evolutionary parameter space of GW150914
to observable space. The contours correspond to the $68\%$ and $95\%$ confidence
intervals. The blue contour is the reprojected posterior after the root-finding
procedure. The orange contour is the reprojected posterior after the MCMC
procedure. The green contour is the posterior plotted using the original LVK
posterior samples. }
\label{fig:GW150914_reprojection}
\script{figure3_sanityCheck.py}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.49\textwidth]{figures/GWTC3_f_acc_mass.pdf}
\caption{ The posterior density in the $m_{1,{\rm GW}}-f_{\rm acc}$ space for
    most of the events in GWTC-3. Note that $m_{1,{\rm GW}}$ here refers to the
    reprojected posterior instead of the posterior released by LIGO. Each
    contour is the $68\%$ credible interval of the posterior density for a
    particular event. At $m_{1,{\rm GW}} \sim 45 M_{\odot}$, the pair
    instability supernova mechanism prevents \texttt{COSMIC} from producing
    events that are more massive than this cutoff. Therefore, events with the
    majority of posterior support above this cutoff are not compatible with
    \texttt{COSMIC}, hence have a large KL divergence and are excluded from this
    figure. On the low mass end, neutron star binaries or neutron star-black
    hole binaries are subjected to randomness induced by the natal kick, also
    resulting in a larger and fluctuating KL divergences, and therefore are also
    excluded from the analysis. }
\label{fig:GWTC-3_f_acc_mass}
\script{figure4_population.py}
\end{figure}
